---
title: "Assignment 5: Working with APIs"
author: "Michal Heydel"
date: "05/11/2017"
output: github_document
---

## Instructions

This file (`Assignment-5.Rmd`) is an RMarkdown file, which is slightly different from a Jupyter notebook.  You will need to open it within [RStudio](https://www.rstudio.com), and compile it to a Markdown file using the **knitr** package.  From RStudio, this is the "Knit" button that appears in the top edge of your Source pane.  When you knit it, `R` will execute the code in your code blocks, and render the output as formatted Markdown (in this example it will `generate Assignment-5.md`).  

There are plenty of instructions about how to use RMarkdown, such as [these](http://rmarkdown.rstudio.com/authoring_rcodechunks.html).  If you define a code block using Python, then any code within that block will be executed in Python.  It works with [other languages](http://rmarkdown.rstudio.com/authoring_knitr_engines.html) too.  

#### Deadline: Wednesday 5pm, 8 November

## Part A: Working with APIs (20 points)

1.  Try using `curl` to get a website from `http://www.example.com`.  This one is provided for you, as an example.  On Windows, you might need to change the language engine to something other than bash.  (See http://rmarkdown.rstudio.com/authoring_knitr_engines.html#bash)
```{r}
# I have done it also in command Prompt in Windows
library(curl)
readLines(curl("http://www.example.com"))

```



2.  Get the information from the [GitHub API](https://developer.github.com/v3/repos/#get) about the [`lse-st445/lectures`](https://github.com/lse-st445/lectures) repository.  You will need to use `curl` for this, but you are welcome to use the [**RCurl**](https://cran.r-project.org/web/packages/RCurl/index.html) package for R, or the [PycURL](http://pycurl.io/docs/latest/) module for Python to do this.  The examples below give you the starter code you need for the R solution.

    Hint: Part of the URL will be `repos/lse-st445`.
    
```{r}
readLines(curl("https://api.github.com/repos/lse-st445/lectures"))
```

```{r}
# INPUT:
# C:\Users\Michal>curl https://api.github.com/repos/lse-st445/lectures
#
#  OUTPUT:
# {
#   "id": 102475502,
#   "name": "lectures",
#   "full_name": "lse-st445/lectures",
#   "owner": {
#     "login": "lse-st445",
#     "id": 31655282,
#     "avatar_url": "https://avatars0.githubusercontent.com/u/31655282?v=4",
#     "gravatar_id": "",
#     "url": "https://api.github.com/users/lse-st445",
#     "html_url": "https://github.com/lse-st445",
#     "followers_url": "https://api.github.com/users/lse-st445/followers",
#     "following_url": "https://api.github.com/users/lse-st445/following{/other_user}",
#     "gists_url": "https://api.github.com/users/lse-st445/gists{/gist_id}",
#     "starred_url": "https://api.github.com/users/lse-st445/starred{/owner}{/repo}",
#     "subscriptions_url": "https://api.github.com/users/lse-st445/subscriptions",
#     "organizations_url": "https://api.github.com/users/lse-st445/orgs",
#     "repos_url": "https://api.github.com/users/lse-st445/repos",
#     "events_url": "https://api.github.com/users/lse-st445/events{/privacy}",
#     "received_events_url": "https://api.github.com/users/lse-st445/received_events",
#     "type": "Organization",
#     "site_admin": false
#   },
#   "private": false,
#   "html_url": "https://github.com/lse-st445/lectures",
#   "description": "ST445 Managing and Visualizing Data",
#   "fork": false,
#   "url": "https://api.github.com/repos/lse-st445/lectures",
#   "forks_url": "https://api.github.com/repos/lse-st445/lectures/forks",
#   "keys_url": "https://api.github.com/repos/lse-st445/lectures/keys{/key_id}",
#   "collaborators_url": "https://api.github.com/repos/lse-st445/lectures/collaborators{/collaborator}",
#   "teams_url": "https://api.github.com/repos/lse-st445/lectures/teams",
#   "hooks_url": "https://api.github.com/repos/lse-st445/lectures/hooks",
#   "issue_events_url": "https://api.github.com/repos/lse-st445/lectures/issues/events{/number}",
#   "events_url": "https://api.github.com/repos/lse-st445/lectures/events",
#   "assignees_url": "https://api.github.com/repos/lse-st445/lectures/assignees{/user}",
#   "branches_url": "https://api.github.com/repos/lse-st445/lectures/branches{/branch}",
#   "tags_url": "https://api.github.com/repos/lse-st445/lectures/tags",
#   "blobs_url": "https://api.github.com/repos/lse-st445/lectures/git/blobs{/sha}",
#   "git_tags_url": "https://api.github.com/repos/lse-st445/lectures/git/tags{/sha}",
#   "git_refs_url": "https://api.github.com/repos/lse-st445/lectures/git/refs{/sha}",
#   "trees_url": "https://api.github.com/repos/lse-st445/lectures/git/trees{/sha}",
#   "statuses_url": "https://api.github.com/repos/lse-st445/lectures/statuses/{sha}",
#   "languages_url": "https://api.github.com/repos/lse-st445/lectures/languages",
#   "stargazers_url": "https://api.github.com/repos/lse-st445/lectures/stargazers",
#   "contributors_url": "https://api.github.com/repos/lse-st445/lectures/contributors",
#   "subscribers_url": "https://api.github.com/repos/lse-st445/lectures/subscribers",
#   "subscription_url": "https://api.github.com/repos/lse-st445/lectures/subscription",
#   "commits_url": "https://api.github.com/repos/lse-st445/lectures/commits{/sha}",
#   "git_commits_url": "https://api.github.com/repos/lse-st445/lectures/git/commits{/sha}",
#   "comments_url": "https://api.github.com/repos/lse-st445/lectures/comments{/number}",
#   "issue_comment_url": "https://api.github.com/repos/lse-st445/lectures/issues/comments{/number}",
#   "contents_url": "https://api.github.com/repos/lse-st445/lectures/contents/{+path}",
#   "compare_url": "https://api.github.com/repos/lse-st445/lectures/compare/{base}...{head}",
#   "merges_url": "https://api.github.com/repos/lse-st445/lectures/merges",
#   "archive_url": "https://api.github.com/repos/lse-st445/lectures/{archive_format}{/ref}",
#   "downloads_url": "https://api.github.com/repos/lse-st445/lectures/downloads",
#   "issues_url": "https://api.github.com/repos/lse-st445/lectures/issues{/number}",
#   "pulls_url": "https://api.github.com/repos/lse-st445/lectures/pulls{/number}",
#   "milestones_url": "https://api.github.com/repos/lse-st445/lectures/milestones{/number}",
#   "notifications_url": "https://api.github.com/repos/lse-st445/lectures/notifications{?since,all,participating}",
#   "labels_url": "https://api.github.com/repos/lse-st445/lectures/labels{/name}",
#   "releases_url": "https://api.github.com/repos/lse-st445/lectures/releases{/id}",
#   "deployments_url": "https://api.github.com/repos/lse-st445/lectures/deployments",
#   "created_at": "2017-09-05T11:56:33Z",
#   "updated_at": "2017-10-12T05:25:05Z",
#   "pushed_at": "2017-10-26T07:07:52Z",
#   "git_url": "git://github.com/lse-st445/lectures.git",
#   "ssh_url": "git@github.com:lse-st445/lectures.git",
#   "clone_url": "https://github.com/lse-st445/lectures.git",
#   "svn_url": "https://github.com/lse-st445/lectures",
#   "homepage": "",
#   "size": 19960,
#   "stargazers_count": 6,
#   "watchers_count": 6,
#   "language": "Jupyter Notebook",
#   "has_issues": true,
#   "has_projects": true,
#   "has_downloads": true,
#   "has_wiki": true,
#   "has_pages": false,
#   "forks_count": 18,
#   "mirror_url": null,
#   "archived": false,
#   "open_issues_count": 1,
#   "forks": 18,
#   "open_issues": 1,
#   "watchers": 6,
#   "default_branch": "master",
#   "organization": {
#     "login": "lse-st445",
#     "id": 31655282,
#     "avatar_url": "https://avatars0.githubusercontent.com/u/31655282?v=4",
#     "gravatar_id": "",
#     "url": "https://api.github.com/users/lse-st445",
#     "html_url": "https://github.com/lse-st445",
#     "followers_url": "https://api.github.com/users/lse-st445/followers",
#     "following_url": "https://api.github.com/users/lse-st445/following{/other_user}",
#     "gists_url": "https://api.github.com/users/lse-st445/gists{/gist_id}",
#     "starred_url": "https://api.github.com/users/lse-st445/starred{/owner}{/repo}",
#     "subscriptions_url": "https://api.github.com/users/lse-st445/subscriptions",
#     "organizations_url": "https://api.github.com/users/lse-st445/orgs",
#     "repos_url": "https://api.github.com/users/lse-st445/repos",
#     "events_url": "https://api.github.com/users/lse-st445/events{/privacy}",
#     "received_events_url": "https://api.github.com/users/lse-st445/received_events",
#     "type": "Organization",
#     "site_admin": false
#   },
#   "network_count": 18,
#   "subscribers_count": 3
# }

```


    
## Part B: Working with Twitter Data (50 points)

1.  Use the **twitteR** package for R to look up the last 2,000 Tweets from [Donald Trump's Twitter feed](https://twitter.com/realDonaldTrump).  Save the output to an object called `trump_tweets`, as a data.frame.

    (Note that in the code block, you will need to change the `eval = FALSE` to `eval = TRUE`.)


```{r, eval = TRUE}
suppressPackageStartupMessages(library(twitteR))
# replace with your credentials
api_key <- "OWea1JDj2RMgv9ktXcKkM3CRI"
api_secret <- "zolroSpEUpqFrTABaVHttXDYrKAIWBBGPpFjXZ5j4r201obVWq"
access_token <- "927171157018759173-tqtWOcZMkWsnCvUToWsR3W0qSp64jwm"
access_token_secret <- "qMvXFuUpsnZD3b2TB1O49aGLSU6p607hDBnzkaYCdJWxR"
    
# authorize the Twitter access
setup_twitter_oauth(api_key, api_secret, access_token, access_token_secret)
    
# use userTimeline()
tw <- userTimeline("realDonaldTrump", n = 2000, includeRts = TRUE)

# use the command from lecture notes to convert result into a data.frame
twDf <- twListToDF(tw)
```
2.  Display the output of the first 20 Tweets.  What sort of returned information is in the result?

```{r}
suppressPackageStartupMessages(library(stringi))
suppressPackageStartupMessages(library(stringr))
#twDf[["text"]] <- stri_enc_toascii(twDf[["text"]])
twDf[1:20, ]
names(twDf) # text of the tweet, Have i favorite it, How many favorites, the location it was sent from, the device it was sent from and much more 
# https://developer.twitter.com/en/docs/tweets/data-dictionary/overview/tweet-object
```




3.  How could we convert the information about the device into a simpler variable, containing just the device?
```{r}
suppressPackageStartupMessages(library(dplyr))
twDf$statusSource <- unlist(str_extract_all(twDf$statusSource, "(?<=>)(.*)(?=<)" ))

colnames(twDf)[10] = "device"
```

```{r}
Source_DT <- table(twDf$device)
Source_DT
```


4.  Use the **quanteda** package to save this to a corpus object, look up the result using the Lexicoder Sentiment dictionary (see `?data_dictionary_LSD2015), and plot the positive versus negative balance using a barplot.

    ```{r, eval = TRUE}
suppressPackageStartupMessages(library("quanteda"))
trump_corpus <- corpus(twDf)
device = docvars(trump_corpus, "device") 
trump_sentiment <- dfm(trump_corpus, groups = device, dictionary = data_dictionary_LSD2015[1:2])
    
# plot a barplot of positive versus negative
trump_sentiment   
```
```{r}
library(ggplot2)
data_plot <- as.data.frame(trump_sentiment)
data_plot$device <- rownames(data_plot)
```
```{r}
library(reshape2)

data_plot_long <- melt(data_plot, id.vars="device", variable.name="State" )

ggplot(data = data_plot_long, aes(x = device, y = value, fill = State) ) + 
  geom_bar(stat="identity", position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Number of words", x = "Device Name") +
  ggtitle("Donald Trump tweets, positive or negative statements?")
```




## Part C: Working with Facebook Data (30 points)

1.  Access the last 20 Facebook posts from [Donald Trump's public page](https://www.facebook.com/DonaldTrump/).  You can find starter code [here](https://github.com/kbenoit/ITAUR/blob/master/6_advanced/social_media_example.R), and you can use this to follow the examples.
```{r}
suppressPackageStartupMessages(library(Rfacebook))
suppressPackageStartupMessages(library(quanteda))   
```

```{r}

# Access token: https://developers.facebook.com/tools/explorer/
token <- "EAACEdEose0cBAGbYoMUZAij52MkZAbwz7OFEi7Ig7B9REiI0DwLgSED2NkLPJQWoXZBI4xp5NvGbZAHlAi50QFm0kFeeAj3Gb1Mksgeu6Y1k079HqU3JMQgQIwpeESv24ZC7A5hfZBhjy1iGfDsLxZAQQmZAlkFNJccvwMwwPrjj5DVhuZCGbDJhu6qqzPzkT8XztlxA4KZBx1BAZDZD"
    
# use getPage() here

Donald_Trump <- getPage('DonaldTrump', token = token, n = 200)
```
    
2.  Display the first 5 posts.
```{r}
head(Donald_Trump,5)
```


3.  (Extra credit)  Do some analysis, plot, or any other analytics with the data from 1 and 2.  You can follow the `social_media_example.R` linked above for inspiration, or even reproduce that.
```{r}

colnames(Donald_Trump)[3]= "text"
#summary(Donald_Trump)
fbcorpus <- corpus(Donald_Trump)
#summary(fbcorpus)

fb_type = docvars(fbcorpus, "type")
trump_type = dfm(fbcorpus, groups = fb_type, dictionary = data_dictionary_LSD2015[1:2])
trump_type
```
```{r}
library(ggplot2)
library(reshape2)
data_type <- as.data.frame(trump_type)
data_type$type <- rownames(trump_type)
```

```{r}


data_type_long <- melt(data_type, id.vars="type", variable.name="State" )

ggplot(data = data_type_long, aes(x = type, y = value, fill = State) ) + 
  geom_bar(stat="identity", position = position_dodge()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Number of words", x = "Type of post") +
  ggtitle("Donald Trump facebook post, positive or negative statements?")
```



```{r}
fb_likes = docvars(fbcorpus, "likes_count")
trump_likes = dfm(fbcorpus, groups = fb_likes, dictionary = data_dictionary_LSD2015[1:2])
trump_likes
```
```{r}
data_likes <- as.data.frame(trump_likes)
data_likes$likes_count <- rownames(data_likes)
data_likes$total_emotions <- data_likes$positive + data_likes$negative


par(mfrow=c(1,3))

plot(data_likes$negative ,data_likes$likes_count)
plot(data_likes$positive ,data_likes$likes_count)
plot(data_likes$total_emotions ,data_likes$likes_count)

# cannot see any linear relationship - no sense for any linear model
```


